An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/7.conclusion.tex
remove not-needed part
change on TODO part
update third part

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs, restriction for $\pginline{Case}$ (shown in Section 4.1). To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more interesting programs for experimental results.

@@

\textcolor{red}{Add here}
Third is introducing type systems to our target language. If we introduce this, we need to investigate more about $construct\_dummy$, because current definition causes type error.

\begin{itemize}
\item $construct\_dummy$??
\end{itemize}

>>>>

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs, restriction for $\pginline{Case}$ (shown in Section 4.1). To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more various programs for experimental results.

@@

Third is introducing type systems to datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. We need to investigate more about $construct\_dummy$, because current definition that is used in Section 6 will cause type errors.

%\begin{itemize}
%\item $construct\_dummy$??
%\end{itemize}
